---
title: "POF Analysis"
author: "Matt Mingay"
output:
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(reshape2)
```

```{r, eval=F, include=F, echo=F}

allpoff <- NULL

url <- read_html("http://ca.pof.com/viewprofile.aspx?profile_id=137056285")

for (i in 1:10000) {
tryCatch({  
  age = url %>% html_node("#age") %>%
    html_text() 
  username = url %>% html_node("#username") %>%
    html_text()
  fishtype = url %>% html_node("#fishtype") %>%
    html_text() 
  smoke = url %>% html_node("#smoke") %>%
    html_text()
  ethnicity = url %>% html_node("#ethnicity") %>%
    html_text()
  zodiac = url %>% html_node("#zodiac") %>%
    html_text()
  bodytype = url %>% html_node("#body") %>%
    html_text()
  temp <- data.frame(fishtype, smoke, age, username, ethnicity, zodiac, bodytype)
  allpoff <- rbind(allpoff, temp)
  urlb <- url %>% html_node("#image-bar > div:nth-child(1)") %>% html_node("a") %>%
    html_attr("href") %>% gsub("\\\r.*", "", .) %>% paste0("http://ca.pof.com/", .)
  url <- read_html(urlb)
  })
  cat(i, "..\r")
}

save(allpoff, file="~/Google Drive/github_share/allpoff_10k.txt")

```

##Filter duplicates

```{r, cache.lazy=T}
load(file="~/Google Drive/github_share/allpoff_10k.txt")
```

#####Number of lines in the collected data
```{r}
nrow(allpoff)
```


#####Number of lines with a unique username from collected data
```{r}
allpof <- tbl_df(allpoff) %>% unique()
nrow(allpof)
```

> looks like there is some redundancy when using the image bar for browsing. Only 3475/10000 of users were unique.

##Count number of different fishtype

```{r, fig.width=7, fig.height=12}
zprop <- tbl_df(allpof) %>% group_by(fishtype) %>% tally()
ggplot(zprop, aes(reorder(fishtype, n), n))+geom_bar(stat="identity")+coord_flip()
```

```{r, eval=F, include=F}
tbl_df(allpof) %>% group_by(fishtype) %>% tally() %>% arrange(n) %>% data.frame() %>% head(n=25)
```

> select those fishtypes with at least 10 occurences for easier downstream visualization 

```{r}
zprop <- tbl_df(allpof) %>% group_by(fishtype) %>% tally() %>% filter(n>9)
```

##Proportion of bodytypes within different fishtypes 

```{r, fig.width=9, fig.height=5}

tbl_df(allpof) %>% group_by(bodytype, fishtype) %>% tally() %>% inner_join(zprop, by="fishtype") %>% mutate(prop=(n.x/n.y)*100) %>% ggplot(aes(x=reorder(fishtype,prop), y=prop, fill=bodytype)) + geom_bar(stat="identity", position="stack") + coord_flip() + xlab('') + ylab("Percentage of Fish")

```

> It looks like gamers, geeks and straight edge women tend to carry a few extra pounds


##Proportion of smoking status within different fishtypes

```{r, fig.width=9, fig.height=5}
tbl_df(allpof) %>% group_by(smoke, fishtype) %>% tally() %>% inner_join(zprop, by="fishtype") %>% mutate(prop=(n.x/n.y)*100) %>% ggplot(aes(x=reorder(fishtype,prop), y=prop, fill=smoke)) + geom_bar(stat="identity", position="stack") + coord_flip() + xlab('') + ylab("Percentage of Fish")
```

> It looks like hippies, daredevil and tatooed fish tend to smoke more often


##Number of fish with different zodiacs

```{r, fig.width=9, fig.height=5}
tbl_df(allpof) %>% group_by(zodiac) %>% tally() %>% ggplot(aes(reorder(zodiac, n), n))+geom_bar(stat="identity")+coord_flip()
zodn <- tbl_df(allpof) %>% group_by(zodiac) %>% tally()
```

> Running low on scorpio

##Number of fish with different ethnicities

```{r, fig.width=9, fig.height=5}
tbl_df(allpof) %>% group_by(ethnicity) %>% tally() %>% ggplot(aes(reorder(ethnicity, n), n))+geom_bar(stat="identity")+coord_flip()
```

> The sea of fish seems to be dominated by caucasians

##How is body type related to ethnicity?

```{r, fig.width=9, fig.height=5}

ethn <- tbl_df(allpof) %>% group_by(ethnicity) %>% tally()

tbl_df(allpof) %>% group_by(bodytype, ethnicity) %>% tally() %>% inner_join(ethn, by="ethnicity") %>% mutate(prop=(n.x/n.y)*100) %>% ggplot(aes(x=ethnicity, y=prop, fill=bodytype)) + geom_bar(stat="identity", position="stack") + coord_flip() + ylab("Percentage of Fish")
```

##Proportion smokers within different bodytype classes

```{r, fig.width=9, fig.height=5}

bodn <- tbl_df(allpof) %>% group_by(bodytype) %>% tally() 

tbl_df(allpof) %>% group_by(bodytype, smoke) %>% tally() %>% inner_join(bodn, by="bodytype") %>% mutate(prop=(n.x/n.y)*100) %>% arrange(-prop) %>% ggplot(aes(x=bodytype, y=prop, fill=smoke)) + geom_bar(stat="identity", position="stack") + coord_flip() + ylab("Percentage of Fish")

```

> I expected to see more thin people who smoke often but this doesn't seem to be the case


#####minumum age
```{r}
#minumum age
min(as.numeric(as.character(allpof$age)))
```

#####maximum age
```{r}
max(as.numeric(as.character(allpof$age)))
```

####Create and group fish into age ranges 

```{r}
agepof <- tbl_df(allpof) %>% mutate(agegroup=cut(as.numeric(as.character(age)), c(17,25,30,50)))
agegro <- tbl_df(agepof) %>% group_by(agegroup) %>% tally()
```

##Proportion of bodytypes within different age groups 

```{r, fig.width=9, fig.height=5}
tbl_df(agepof) %>% group_by(bodytype, agegroup) %>% tally() %>% inner_join(agegro, by="agegroup") %>% mutate(prop=(n.x/n.y)*100) %>% ggplot(aes(x=reorder(agegroup,prop), y=prop, fill=bodytype)) + geom_bar(stat="identity", position="stack") + coord_flip() + xlab('') + ylab("Percentage of Fish")

```

> Age group doesn't seem to contribute very much to bodytype
